Spanner: Google's Globally-Distributed Database \newline Seminar Report

### 2016-02-16 paper/paper.tex
Iterate Directories

A directory is the unit of data placement/movement, hence only whole directories
are moved between Paxos groups, even across zones. Figure~\ref{subfig:directories}
illustrates this principle. Directory 2 is moved from Paxos group 1 to Paxos group
2 and at the same time from zone 2 to zone 3. Google shortly mentions that this
is an over-simplified view because a directory is split into multiple
\emph{fragments} if it grows too large. However, Google does not provide more
details.

All the data within a directory has the same replication configuration. As will
be described later, the concept of directories enables Google to improve the
performance of Spanner by placing directories in the same Paxos group which are
frequently accessed together. The fact that in general multiple directories are
placed in the same Paxos group is another difference between the key-value mapping
of Spanner and the one used in Bigtable. A Spanner tablet may contain multiple
contiguous ranges of keys (= directories) as opposed to a Bigtable tablet which
may only contain one contiguous range of keys. Figure~\ref{fig:comparison-tablets}
shows an example comparison of the two tablet types.

\begin{figure}[ht]
  \centering
  \begin{subfigure}{0.45\textwidth}
    \centering
    \begin{tabular}{|l||ll}
      \hline
      {\bfseries Key} & {\bfseries Value} \tabularnewline
      \hline\hline
      12341 & \ldots & \rdelim\}{3}{5mm}[Directory 1234] \tabularnewline
      12342 & \ldots \tabularnewline
      12343 & \ldots \tabularnewline
      \hline
      67891 & \ldots & \rdelim\}{4}{3mm}[Directory 6789] \tabularnewline
      67892 & \ldots \tabularnewline
      67893 & \ldots \tabularnewline
      67894 & \ldots \tabularnewline
      \hline
    \end{tabular}
    \caption{Spanner tablet}
    \label{subfig:spanner-tablet}
  \end{subfigure}
  \qquad
  \begin{subfigure}{0.45\textwidth}
    \centering
    \begin{tabular}{|l||l}
      \hline
      {\bfseries Key} & {\bfseries Value} \tabularnewline
      \hline\hline
      12341 & \ldots \tabularnewline
      12342 & \ldots \tabularnewline
      12343 & \ldots \tabularnewline
      12344 & \ldots \tabularnewline
      12345 & \ldots \tabularnewline
      12346 & \ldots \tabularnewline
      12347 & \ldots \tabularnewline
      \hline
    \end{tabular}
    \caption{Bigtable tablet}
    \label{subfig:bigtable-tablet}
  \end{subfigure}
  \caption{Comparison of Spanner's and Bigtable's tablets}
  \label{fig:comparison-tablets}
\end{figure}

This partitioning of the row space is critical for the performance of Spanner
because it allows Google to physically \emph{co-locate} data that is frequently
accessed together. Therefore, directories are the smallest unit for which an
application/user can specify geographic-replication properties. An application
can control replication in two dimension, i.e. the number and types of replicas,
and, the geographic placement of replicas.

>>>>

A directory is the unit of data placement/movement, hence only whole directories
are moved between Paxos groups, even across zones. Figure~\ref{subfig:directories}
illustrates this principle. Directory 2 is moved from Paxos group 1 to Paxos group
2 and, at the same time, from zone 2 to zone 3. Google shortly mentions that this
is an over-simplified view because a directory is split into multiple
\emph{fragments} if it grows too large. However, Google does not provide any
additional details.

All the data within a directory has the same replication configuration. As will
be described later, the concept of directories enables Google to improve the
performance of Spanner by placing directories which are frequently accessed
together in the same Paxos group. The fact that in general multiple directories
are placed in the same Paxos group is another difference between the key-value
mapping of Spanner and the one used in Bigtable. A Spanner tablet may contain
multiple contiguous ranges of keys (= directories) as opposed to a Bigtable tablet
which may only contain one contiguous range of keys.
Figure~\ref{fig:comparison-tablets} shows an example comparison of the two tablet
types.

\begin{figure}[ht]
  \centering
  \begin{subfigure}{0.45\textwidth}
    \centering
    \begin{tabular}{|l||ll}
      \hline
      {\bfseries Key} & {\bfseries Value} \tabularnewline
      \hline\hline
      12341 & \ldots & \rdelim\}{3}{5mm}[Directory 1234] \tabularnewline
      12342 & \ldots \tabularnewline
      12343 & \ldots \tabularnewline
      \hline
      67891 & \ldots & \rdelim\}{4}{3mm}[Directory 6789] \tabularnewline
      67892 & \ldots \tabularnewline
      67893 & \ldots \tabularnewline
      67894 & \ldots \tabularnewline
      \hline
    \end{tabular}
    \caption{Spanner tablet}
    \label{subfig:spanner-tablet}
  \end{subfigure}
  \qquad
  \begin{subfigure}{0.45\textwidth}
    \centering
    \begin{tabular}{|l||l}
      \hline
      {\bfseries Key} & {\bfseries Value} \tabularnewline
      \hline\hline
      12341 & \ldots \tabularnewline
      12342 & \ldots \tabularnewline
      12343 & \ldots \tabularnewline
      12344 & \ldots \tabularnewline
      12345 & \ldots \tabularnewline
      12346 & \ldots \tabularnewline
      12347 & \ldots \tabularnewline
      \hline
    \end{tabular}
    \caption{Bigtable tablet}
    \label{subfig:bigtable-tablet}
  \end{subfigure}
  \caption{Comparison of Spanner's and Bigtable's tablet}
  \label{fig:comparison-tablets}
\end{figure}

This partitioning of the row space is critical for the performance of Spanner
because it allows Google to physically \emph{co-locate} data that is frequently
accessed together. Therefore, directories are the smallest unit for which an
application/user can specify geographic-replication properties. An application
can control replication in two dimensions, namely the number and types of
replicas, and the geographic placement of replicas.
